\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/BadUSBC.tex
gramarly abstract and intro

The security of \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused serious problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising normal \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of user interface to conduct precise attacks as well as get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new features of \ac{USB} Type-C and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

>>>>

The security of the \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused severe problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

### 2021-03-10 WOOT/Files/introduction.tex
gramarly abstract and intro

The \ac{USB} protocol has become popular around the world
since its appearance, as it provides a unified and easy-to-use approach for a
large range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

On the other side of the coin, the security of \ac{USB} has caused serious problems.
The designers of the \ac{USB} protocol did not care much about security issues as
they wanted to make an easy-to-use protocol.  There are more than 400
vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted through modification of the device firmware, which will disguise
normal \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend themselves as normal users, typing malicious commands to
victim computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily escape from traditional
anti-virus software since it is hard to distinguish them from normal \ac{USB}
devices.

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status which limits
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns like buttons and links on victim
computers by disguising \ac{USB} devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the usage of the host network.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a larger range of
peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID} like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass some countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
10 volunteers are involved in the user study.
At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing work of \ac{USB} security from the aspects of attacking and
defense respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

>>>>

The \ac{USB} protocol has become popular worldwide
since its appearance, as it provides a unified and easy-to-use approach for a
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

On the other side of the coin, the security of \ac{USB} has caused severe problems.
Recent research of all USB specifications indicates that security has not been taken into consideration.~\cite{sok}  There are more than 400
vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted by modifying the device firmware, which will disguise
 as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend themselves as regular users, typing malicious commands to
victim computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily escape from traditional
anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
devices.

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status, limiting
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns like buttons and links on victim
computers by disguising \ac{USB} devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the host network usage.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a more extensive range of
peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID} like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass some countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers are involved in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing work of \ac{USB} security from the aspects of attacking and
defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}
